OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2017-11-24 manuscript_nar.tex
Changing to NAR references

To test the correction of biases, we gathered a set of
published \citep{ledily2014distinct, encode2012integrated, rao20143d,
stadhouders2017transcription, lin2012global, dixon2012topological} and
unpublished Hi-C data of different cell types and organisms
(Supplementary Table~1).

@@

All data were processed through a pipeline based on TADbit
\citep{serra2016structural}. Briefly, after controlling the quality of
FASTQ files, paired-end reads were mapped to the corresponding reference
genome (hg38 and mm10) taking into account the restriction enzyme site.
Non-informative contacts were removed applying the following TADbit
filters: \texttt{self-circle}, \texttt{dangling-ends}, \texttt{error},
\texttt{extra-dangling-ends}, \texttt{duplicated} and
\texttt{random-breaks}. For more details, see the methods section of
\cite{stadhouders2017transcription}. In addition, the pipeline is
available from the Supplementary Material published by
\cite{quilez2017managing}.

@@

\bibliographystyle{natbib}
\bibliography{references}

>>>>

To test the correction of biases, we gathered a set of
published \citep[][BioRxiv: https://doi.org/10.1101/132456]{ledily2014distinct, encode2012integrated, rao20143d,
lin2012global, dixon2012topological} and
unpublished Hi-C data of different cell types and organisms
(Supplementary Table~1).

@@

All data were processed through a pipeline based on TADbit
\citep{serra2016structural}. Briefly, after controlling the quality of
FASTQ files, paired-end reads were mapped to the corresponding reference
genome (hg38 and mm10) taking into account the restriction enzyme site.
Non-informative contacts were removed applying the following TADbit
filters: \texttt{self-circle}, \texttt{dangling-ends}, \texttt{error},
\texttt{extra-dangling-ends}, \texttt{duplicated} and
\texttt{random-breaks}. For more details, see the methods section of
(BioRxiv: https://doi.org/10.1101/132456). In addition, the pipeline is
available from the Supplementary Material published by
\cite{quilez2017managing}.

@@

\bibliographystyle{nar}
\bibliography{references}
